Universal Anonymous Signatures

### 2022-05-28 prism-backend/research/gsac/app-model-related.tex
Added proofs for GS-MDO and DAC special cases.

      \procedure[linenumbering]{$\Exp^{frame}_{\adv,gs}(1^\secpar)$}{%
        (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
        (\msg,\sig,\upk,\tau) \gets \adv^{\mathcal{O}^{frame}}
        (\gpk,\osk,\isk) \\
        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
        \pcreturn 1~\pcif \upk \in \HU \land \PRVUK[\upk] \neq \bot \land
        \Judge(\gpk,\upk,\msg,\sig,\tau) = 1~\land \\
        \pcind \adv~\textrm{did not query}~USK(\upk)~\textrm{or}~
        GSig(\PRVUK[\upk],\msg) \\
        \pcreturn 0
      }       
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.55\textwidth}
      \procedure[linenumbering]{$\Exp^{trace}_{\adv,gs}(1^\secpar)$}{%
        (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
        (\msg,\sig) \gets \adv^{\mathcal{O}^{trace}}(\gpk,\osk) \\
        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
        (\upk, \tau) \gets \Open(\gpk,\osk,\trans,\msg,\sig) \\
        \pcif \upk \notin \HU \cup \CU \lor \Judge(\gpk,\upk,\msg,\sig,\tau)
        = 0: \\ 
        \pcind \pcreturn 1 \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for group signatures \cite{bsz05}, only with minor    
    ``harmless'' edits to compare easier with \CUASGS. Concretely, since we
    output {\upk}s instead of indexes, $i=0$ in the traceability game now reads
    $\upk \notin \HU \cup \CU$. For the oracles' definitions, check the
    referenced paper.
    $\mathcal{O}^{anon} \gets \lbrace Ch,Open,SndToU,WReg,USK,CrptU \rbrace$,
    $\mathcal{O}^{trace} \gets \lbrace SndToI,AddU,RReg,USK,CrptU \rbrace$,
    and $\mathcal{O}^{frame} \gets \lbrace SndToU,WReg,GSig,USK,CrptU \rbrace$.
  }
  \label{fig:model-gs}  
\end{figure}

@@

\begin{theorem}[Non-frameability of \CUASGS]
  If the base \CUASGen construction is non-frameable according to
  \defref{def:frame-uas}, then \CUASGS is a traceable group signature
  scheme.
\end{theorem}

@@

@@

\begin{description}  
\item[$\parm \gets \Setup(\secpar,\AttrSpace)$.] As in \CUASGen, but using
  $\NIZKRel_{\Sign-prv}$ instead of $\NIZKRel_{\Sign}$.  
\item[$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.] As in \CUASGen, using
  $\fissue^{\sring}$.  
\item[$(\opk,\osk) \gets \OKeyGen(\parm,\finsp).$] As in \CUASGen, where every
  opener that wants to be a valid opener in \CUASRing, needs to set \finsp to
  $\finsp^0$.  
\item[$\usk \gets \UKeyGen(\parm).$] Can only be run after \IKeyGen. Let 
  $\usk \gets \isk$.
\item[$\langle \cred,\bot,\utrans,\bot \rangle \gets
  \langle \Obtain(\usk,\scred,\attrs),\Issue(\isk,\sipk,\attrs)\rangle.$]
  The user picks a ring from an (publicly) available list of issuers (users),
  i.e. $\sring \gets \lbrace \ipk_i \rbrace_{i \in [t]}$, for some $t$. Then,
  runs the $\langle \Obtain,\Issue \rangle$ protocol as in \CUASGen, acting both
  as user and as issuer, and using $\fissue^{\sring}$ as issuance function.
  \attrs are the public keys of the users (issuers) to be included in the ring.
\item[$(\sig,\yeval) \gets \Sign(\usk,\opk,\scred,\msg,\feval).$] As in
  \CUASGen, using $\feval^{\attrs}$ as sign evaluation function, using
  as credential for signing the credential used in the desired $\langle \Obtain,
  \Issue \rangle$ protocol and, as \opk, any previously registered \opk (i.e.,
  such that $\finsp=\finsp^0$).
\item[$1/0 \gets \Verify(\opk,\sipk,\sig,\yeval,\msg,\feval).$] As in \CUASGen.
  Note that $\sipk = \sring$, and $\feval=\feval^{\attrs}$.
\item[$\Open$ and $\Judge$.] As in \CUASGen. Note that $\finsp=\finsp^0$.
\end{description}

@@

@@

\begin{description}
\item[$\parm \gets \Setup(1^\secpar)$.] Runs \Setup from our \CUASGen
  construction.
\item[$(\opk,\osk) \gets OrgKeyGen(\parm)$.] Runs \IKeyGen from our
  \CUASGen construction, setting $\fissue^1$ as issuance function.
\item[$(\upk,\usk) \gets UserKeyGen(\opk)$.] Runs \UKeyGen from the
  \CUASGen construction, and computes $\CCommit(\usk;0)$ as \upk.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\opk,\attrs),\Issue(\osk,\upk,\attrs) \rangle$.]
  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGen, using
  $\fissue^1$ as issuance function.
\item[$1/0 \gets \langle Show(\opk,\attrs,\dattrs,\cred),
  \Verify(\opk,\dattrs) \rangle$.]
  Runs the interactive extension of \Sign and \Verify of the \CUASGen protocol,
  using $\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as
  open function.
\end{description}

@@

>>>>

      \procedure[linenumbering]{$\Exp^{frame}_{\adv,gs}(1^\secpar)$}{%
        (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
        (\msg,\sig,\upk,\tau) \gets \adv^{\mathcal{O}^{frame}}
        (\gpk,\osk,\isk) \\
        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
        \pcreturn 1~\pcif \upk \in \HU \land \PRVUK[\upk] \neq \bot \land
        \Judge(\gpk,\upk,\msg,\sig,\tau) = 1~\land \\
        \pcind \adv~\textrm{did not query}~USK(\upk)~\textrm{or}~
        GSig(\PRVUK[\upk],\msg) \\
        \pcreturn 0
      }       
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.55\textwidth}
      \procedure[linenumbering]{$\Exp^{trace}_{\adv,gs}(1^\secpar)$}{%
        (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
        (\msg,\sig) \gets \adv^{\mathcal{O}^{trace}}(\gpk,\osk) \\
        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
        (\upk, \tau) \gets \Open(\gpk,\osk,\trans,\msg,\sig) \\
        \pcif \upk \notin \HU \cup \CU \lor \Judge(\gpk,\upk,\msg,\sig,\tau)
        = 0: \\ 
        \pcind \pcreturn 1 \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for group signatures \cite{bsz05}, only with minor    
    ``harmless'' edits to compare easier with \CUASGS. Concretely, since we
    output {\upk}s instead of indexes, $i=0$ in the traceability game now reads
    $\upk \notin \HU \cup \CU$. For the oracles' definitions, check the
    referenced paper.
    $\mathcal{O}^{anon} \gets \lbrace Ch,Open,SndToU,WReg,USK,CrptU \rbrace$,
    $\mathcal{O}^{trace} \gets \lbrace SndToI,AddU,RReg,GSig,USK,CrptU \rbrace$,
    and $\mathcal{O}^{frame} \gets \lbrace SndToU,WReg,GSig,USK,CrptU \rbrace$.
  }
  \label{fig:model-gs}  
\end{figure}

@@

\begin{theorem}[Non-frameability of \CUASGS]
  If the base \CUASGen construction is non-frameable according to
  \defref{def:frame-uas}, then \CUASGS is a non-frameable group signature
  scheme.
\end{theorem}

@@

We cannot build the exact same functionality, nor follow the exact same security
model as in the group signatures with message dependent opening (GS-MDO) scheme
described in \cite{ehk+19}. Simply because, therein, the opening functionality
is divided in two authorities: the admitter, who decides which messages are
subject to be opened or not, and generates a token that enables opening
signatures over such messages; and the opener, who performs the actual opening,
but cannot do it without the tokens generated by the admitter. Intuitively, this
can be seen as a sort of ``distribution'' of the opening capability. We define
a variant of this model in which the admitter and opener are combined back into
one entity (the opener), who can only open signatures over predefined messages,
but cannot open any other signature. Moreover, our variant directly supports the
scenario of multiple such openers, each being able to open only signatures
over different messages. Note that it would not be hard to apply thresholding
techniques to extend this case so that our ``unified'' opener role is shared
across multiple entities, who have to cooperate in order to open a signature
\needcite, thus achieving something very close ``in spirit'' to the scheme in
\cite{ehk+19}. In addition, while \cite{ehk+19} follows the static group
signature setting, we move to the dynamic one. Informally, our variant of GS-MDO
is composed of the following algorithms: \Setup,
\IKeyGen, \OKeyGen, \UKeyGen, \Sign, \Verify, \Open; as well as the $\langle
\Obtain, \Issue \rangle$ interactive protocol. \OKeyGen generates an opening
key pair which is already configured to open signatures only over some fixed
(but arbitrary) set of messages. The remaining algorithms are as usual, so we
defer a more detailed description to the construction. The oracles are the same
as in \UAS. The resulting security model is given in \figref{fig:model-gsmdo},
which we adapt from \cite{ehk+19}.

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.45\textwidth}        
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,gsmdo}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (\ipk,\isk) \gets \IKeyGen(\parm) \\
        b^* \gets \adv^{\mathcal{O}^{anon}}(\parm,\ipk) \\
        \pcreturn b^*
      }

      \procedure[linenumbering]{$\Exp^{frame}_{\adv,gsmdo}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (\ipk,\isk) \gets \IKeyGen(\parm) \\
        (\msg,\sig,\upk,\tau) \gets \adv^{\mathcal{O}^{frame}}
        (\ipk,\isk) \\
        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
        \pcreturn 1~\pcif \upk \in \HU \land \PRVUK[\upk] \neq \bot \land
        \Judge(\gpk,\upk,\msg,\sig,\tau) = 1~\land \\
        \pcind \adv~\textrm{did not query}~USK(\upk)~\textrm{or}~
        GSig(\PRVUK[\upk],\msg) \\
        \pcreturn 0
      }       
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.55\textwidth}
      \procedure[linenumbering]{$\Exp^{trace}_{\adv,gsmdo}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (\ipk,\isk) \gets \IKeyGen(\parm) \\
        (\msg,\sig,\upk,\tau) \gets \adv^{\mathcal{O}^{trace}}
        (\ipk,\opk,\osk) \\
        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
        (\upk, \tau) \gets \Open(\gpk,\osk,\trans,\msg,\sig) \\
        \pcif \upk \notin \HU \cup \CU \lor \Judge(\gpk,\upk,\msg,\sig,\tau)
        = 0: \\ 
        \pcind \pcreturn 1 \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for our GS-MDO variant.
    $\mathcal{O}^{anon} \gets \lbrace \OGEN^{\smsg},\HUGEN,\CUGEN,\WREG,
    \OBTAIN,\SIGN,\OPEN,\CHALb \rbrace$; $\mathcal{O}^{trace} \gets \lbrace
    \OGEN,\HUGEN,\CUGEN,\ISSUE,\OBTISS,\RREG,\SIGN \rbrace$;
    $\mathcal{O}^{frame} \gets \lbrace \OGEN,\HUGEN,\CUGEN,\WREG,
    \OBTAIN,\SIGN \rbrace$. $\OGEN^{\smsg}$ is like \OGEN, but only accepting
    functions of type $\finsp^{\smsg}$.
  }
  \label{fig:model-gsmdo}  
\end{figure}

\subsubsection{\CUASGSMDO construction.} %
We show that, as specified in \tabref{tab:uas-alt-funcs}, our \CUASGen
construction for \UAS, restricted to $\fissue^1$ as issuance function,
$\feval^0$ as signature evaluation function, and $\finsp^{\smsg}$ as opening
function, is a secure group signature scheme with message dependent opening
as modelled in \figref{fig:model-gsmdo}. We first quickly define the algorithms,
and then prove security.

\begin{description}
\item[$\parm \gets \Setup(1^\secpar)$.] Like in vanilla \CUASGen.
\item[$(\upk,\usk) \gets \UKeyGen(1^\secpar)$.] Like the \UKeyGen function for
  \CUASGS, in \secref{sapp:related-models-gs}.
\item[$\langle \cred,\utrans \rangle \gets
  \langle\Obtain(\usk,\ipk),\Issue(\isk,\upk)\rangle$.] Like the corresponding
  protocol in in vanilla \CUASGS, \secref{sapp:related-model-gs}.
\item[$\sig \gets \Sign(\gpk,\cred,\msg)$.] Like in vanilla \CUASGen, limited
  on evaluation functions $\feval^0$ and opening functions $\finsp^{\smsg}$.
\item[$1/0 \gets \Verify(\gpk,\sig,\msg)$.] Like in vanilla \CUASGen.
\item[$(\upk,\pi) \gets \Open(\gpk,\osk,\trans,\sig,\msg)$.] Like in vanilla
  \CUASGen.
\item[$1/0 \gets \Judge(\gpk,\pi,\upk,\sig,\msg)$.] Like in vanilla \CUASGen.
\end{description}

\paragraph{Security of \CUASGSMDO.} %
Our \CUASGSMDO construction is a secure group signature scheme,
according to the model in \figref{fig:model-gsmdo}, if the underlying \CUASGen
construction is secure.

Note that both  model construction are essentially restrictions to the model
and construction of \CUASGen. Thus, security directly follows from security of
\CUASGen.

% \begin{theorem}[Anonymity of \CUASGSMDO]
%   If the base \CUASGen construction is anonymous according to
%   \defref{def:anonymity-uas}, then \CUASGSMDO is an anonymous group signature
%   scheme.
% \end{theorem}

% \begin{proof}

%   \qed
% \end{proof}

% \begin{theorem}[Traceability of \CUASGSMDO]
%   If the base \CUASGen construction has unforgeable signing according to
%   \defref{def:sign-forge-uas}, then \CUASGSMDO is a traceable group signature
%   scheme.
% \end{theorem}

% \begin{proof}
%   Traceability follows directly from the corresponding proof for \CUASGS.
%   \qed
% \end{proof}

% \begin{theorem}[Non-frameability of \CUASGSMDO]
%   If the base \CUASGen construction is non-frameable according to
%   \defref{def:frame-uas}, then \CUASGSMDO is a non-frameable group signature
%   scheme.
% \end{theorem}

% \begin{proof}
%   Non-frameability follows directly from the corresponding proof for \CUASGS.
%   \qed
% \end{proof}

@@

\begin{description}  
\item[$\parm \gets \Setup(\secpar,\AttrSpace)$.] As in \CUASGen, but using
  $\NIZKRel_{\Sign-prv}$ instead of $\NIZKRel_{\Sign}$.  
\item[$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.] As in \CUASGen, using
  $\fissue^{\sring}$.  
\item[$(\opk,\osk) \gets \OKeyGen(\parm,\finsp).$] As in \CUASGen, where every
  opener that wants to be a valid opener in \CUASRing, needs to set \finsp to
  $\finsp^0$.  
\item[$\usk \gets \UKeyGen(\parm).$] Can only be run after \IKeyGen. Let 
  $\usk \gets \isk$.
\item[$\langle \cred,\bot,\utrans,\bot \rangle \gets
  \langle \Obtain(\usk,\scred,\attrs),\Issue(\isk,\sipk,\attrs)\rangle.$]
  The user picks a ring from an (publicly) available list of issuers (users),
  i.e. $\sring \gets \lbrace \ipk_i \rbrace_{i \in [t]}$, for some $t$. Then,
  runs the $\langle \Obtain,\Issue \rangle$ protocol as in \CUASGen, acting both
  as user and as issuer, and using $\fissue^{\sring}$ as issuance function.
  \attrs are the public keys of the users (issuers) to be included in the ring.
\item[$(\sig,\yeval) \gets \Sign(\usk,\opk,\scred,\msg,\feval).$] As in
  \CUASGen, using $\feval^{\attrs}$ as sign evaluation function, using
  as credential for signing the credential obtained in the desired $\langle
  \Obtain,\Issue \rangle$ session and, as \opk, any previously registered \opk
  (i.e., such that $\finsp=\finsp^0$).
\item[$1/0 \gets \Verify(\opk,\sipk,\sig,\yeval,\msg,\feval).$] As in \CUASGen.
  Note that $\sipk = \sring$, and $\feval=\feval^{\attrs}$.
\item[$\Open$ and $\Judge$.] As in \CUASGen. Note that $\finsp=\finsp^0$.
\end{description}

@@

\todo{Naming gets a bit confusing here, as \cite{fhs19} use \opk as ``organization
  public key'' and we use it as ``opener public key'', etc. Make some renaming
  (probably, adopt our naming convention).}

@@

\begin{description}
\item[$\parm \gets \Setup(1^\secpar)$.] Runs $\parm' \gets \Setup(1^\secpar)$
    and $(\opk',\osk') \gets \OKeyGen(\parm',\finsp^0)$ from our \CUASGen
    construction. Returns $\parm \gets (\parm',\opk')$.
\item[$(\opk,\osk) \gets OrgKeyGen(\parm)$.] Runs \IKeyGen from our
  \CUASGen construction, setting $\fissue^1$ as issuance function.
\item[$(\upk,\usk) \gets UserKeyGen(\opk)$.] Runs \UKeyGen from the
  \CUASGen construction, and computes $\CCommit(\usk;0)$ as \upk.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\opk,\attrs),\Issue(\osk,\upk,\attrs) \rangle$.]
  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGen, using
  $\fissue^1$ as issuance function.
\item[$1/0 \gets \langle Show(\opk,\attrs,\dattrs,\cred),
  \Verify(\opk,\dattrs) \rangle$.]
  Runs the interactive extension of \Sign and \Verify of the \CUASGen protocol,
  using $\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as
  open function, with $\opk'$ from \parm as opener public key.
\end{description}

@@

We give a simple definition for delegatable anonymous credentials extending
the anonymous credential model in \cite{fhs19}. Next, we briefly describe a
construction based on $(\fissue^n,\feval^{n,\dattrs},\finsp^0)$-\CUASGen, and
show that it satisfies our basic notion of delegatable anonymous credentials.
Roughly, a delegatable anonymous credential scheme is an anononymous credential
scheme in which every issuer of level $n$ can only issue credentials of level
$n+1$. For simplicity, we restrict to the case of using only one credential per
signature, but the generalization is trivial. Note that, in addition to the
algorithms in \secref{sapp:related-models-ac}, we add a helper function $level$
which, given an issuer's public key and its alleged level, returns $1$ if the
level is correct, or $0$ otherwise.

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.4\textwidth}        
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,dac}(1^\secpar)$}{%
        b^* \gets \adv^{HU,CU,obtain,Show,LoR} \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.6\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,dac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\        
        (D,n+1,\st) \gets \adv^{HU,CU,ObtIss,Issue,Show}(\opk) \\
        (\cdot,b) \gets \langle \adv(\st),\Verify(\opk,
        D \cup \lbrace n+1 \rbrace)\rangle \\
        \pcif b = 0: \pcreturn 0 \\
        \pcif(\forall j: \OWNR[j] \in \CU \implies D \cup \lbrace n+1 \rbrace
        \not\subseteq \ATTR[j])~\lor\\
        \pcind level(\opk,n) = 0: \pcreturn 1 \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for delegatable anonymous credentials with selective
    disclosure based on \cite{fhs19}. \OWNR and \ATTR tables are essentially as
    in \secref{ssec:model-uas}. $level(\opk,n)$ is a helper function that
    returns the $1$ if the level of \opk is $n$, or $0$ otherwise.}
  \label{fig:model-dac}  
\end{figure}

\subsubsection{\CUASDAC Construction.} %
We adopt the simplification that the level of an issuer is encoded in its public
key, and anybody can check the issuer's level via some publicly accessible
mechanism. This can be ensured, e.g., by having each issuer post its
  public key along with a proof of ownership of a level $n$ credential -- which
  can be trivially done in \CUASGen.

  \begin{description}
  \item[$\parm \gets \Setup(1^\secpar)$.] As in \CUASAC.
\item[$(\opk,\osk) \gets OrgKeyGen(\parm)$.] Runs a variant of \IKeyGen from
  our \CUASGen construction where, instead of using a conventional signature
  scheme, the issuer leverages its own anonymous credential of level $n$ to
  create a signature in which it only reveals the credential level. That is,
  $\sig_{is} \gets \CUASGen.Sign(\isk,\opk',\cred,\msg_{is},\feval^{0,n})$,
  for some random $\msg_{is}$, and $\opk'$ from \parm, where $\feval^{0,n}$ is a
  signing evaluation function that reveals no attribute other than the level
  of the credential. Let $\opk_{n-1}$ be the issuer of the credential \cred
  (i.e., an issuer with level $n-1$). The current issuer of level $n$ publishes
  its public key as $(\opk_{n-1},\fissue^n,\sig_{is},\msg_{is})$.
\item[$(\upk,\usk) \gets UserKeyGen(\opk)$.] As in \CUASAC.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\opk,\attrs),\Issue(\osk,\upk,\attrs) \rangle$.]
  As in \CUASAC.
\item[$1/0 \gets \langle Show(\opk,\attrs,\dattrs,\cred),
  \Verify(\opk,\dattrs) \rangle$.]
  As in \CUASAC, but using $\feval^{\dattrs,n}$ as signature evaluation
  function.
\end{description}

\paragraph{Security of \CUASDAC.} %
We need to define $level(\opk,n)$. This function first parses \parm
as $(\parm',\opk')$, and \opk as $(\opk_{n-1},\fissue^n,\sig_{is},\msg_{is})$,
and returns $\CUASGen.Verify(\opk_{n-1},\opk',\sig_{is},n,\msg_{is},
\feval^{0,n})$.

Given $level$, the security proofs are as for \CUASAC, with the addition that,
in the unforgeability game, an adversary winning because of $level(\opk,n) = 0$
can be directly used to break the sign unforgeability property of the underlying
\CUASGen scheme.

### 2022-05-28 prism-backend/research/gsac/transformations-uas.tex
Added proofs for UAS => GS and UAS => AC.
Added proofs for GS-MDO and DAC special cases.

\begin{table}[ht!]
  \begin{tabular}{c | c | c | c | c | c}
    \bf Target scheme & \bf $\NIZKRel_{\Sign}$ variant & \bf \fissue variant & \bf \feval variant & \bf \finsp variant & \bf  Defined in \\
    \hline
    \GSAC & None & $\fissue^1$ & $\feval^{\dattrs}$ & $\finsp^{\upk}$
    & \secref{ssec:uas-gsac} \\
    \bf GS-MDO & None & $\fissue^1$ & $\feval^0$ & $\finsp^{\smsg}$
    & \secref{ssec:uas-gsmdo} \\
    \bf Ring sigs. & $\NIZKRel_{\Sign-prv}$ & $\fissue^{\sring}$ & $\feval^{\attrs}$ & $\finsp^0$ & \secref{ssec:uas-ring} \\
    \bf MPS\footnote{Building MPS from \UAS also requires a simple definitional change. See
    \secref{ssec:uas-mps}.} & $\NIZKRel_{\Sign-enc}$ & Any & $\feval^{enc}$ & Any & \secref{ssec:uas-mps} \\
    \bf Delegatable creds & None & $\fissue^n$ & Any & Any & \secref{ssec:uas-delcred} \\
  \end{tabular}
  \caption{How to build related schemes from \UAS.}
  \label{tab:uas-alt-funcs}
\end{table}

@@

Building delegatable credentials is also straightforward, thanks to the \fissue
function. For instance, take the simplification of level-based delegation, where
the owner of a credential of level $n$ can only issue credentials of level
$n+1$. Without loss of generality, assume that the credential level is encoded
in the first attribute of the credential (after the \usk), which we denote with
$a_1$. In this context, any owner of a credential of level $n$ can define an
issuance function $\fissue^n$, as in \eref{eq:uas-delcred-func}.

\begin{align}
  \fissue^n \coloneqq \lbrace \pcif a_1 = n+1: \pcreturn 1;
  \pcelse \pcreturn 0 \rbrace \label{eq:uas-delcred-func}
\end{align}

>>>>

\begin{table}[ht!]
  \begin{tabular}{c | c | c | c | c | c}
    \bf Target scheme & \bf $\NIZKRel_{\Sign}$ variant & \bf \fissue variant & \bf \feval variant & \bf \finsp variant & \bf  Defined in \\
    \hline
    GS & None & $\fissue^1$ & $\feval^0$ & $\finsp^{\upk}$ & Implied by \GSAC \\
    AC\footnote{We show how to build ACs with selective disclosure, but ACs for
    arbitrary claims are direct too.} & None & $\fissue^1$ & $\feval^{\dattrs}$ & $\finsp^0$ & Implied by \GSAC \\
    \GSAC & None & $\fissue^1$ & $\feval^{\dattrs}$ & $\finsp^{\upk}$
    & \secref{ssec:uas-gsac} \\
    \bf GS-MDO\footnote{We achieve something similar to GS-MDO, but not the
    exact same model as in \cite{ehk+19}} & None & $\fissue^1$ & $\feval^0$ & $\finsp^{\smsg}$
    & \secref{ssec:uas-gsmdo} \\
    \bf Ring sigs. & $\NIZKRel_{\Sign-prv}$ & $\fissue^{\sring}$ & $\feval^{\attrs}$ & $\finsp^0$ & \secref{ssec:uas-ring} \\
    \bf MPS\footnote{Building MPS from \UAS also requires a simple definitional change. See
    \secref{ssec:uas-mps}.} & $\NIZKRel_{\Sign-enc}$ & Any & $\feval^{enc}$ & Any & \secref{ssec:uas-mps} \\
    \bf Delegatable creds & None & $\fissue^n$ & $\feval^n$ & Any & \secref{ssec:uas-delcred} \\
  \end{tabular}
  \caption{How to build related schemes from \UAS.}
  \label{tab:uas-alt-funcs}
\end{table}

@@

Building delegatable credentials is also straightforward, thanks to the \fissue
and \feval functions. For instance, take the simplification of level-based
delegation, where the owner of a credential of level $n$ can only issue
credentials of level $n+1$. Without loss of generality, assume that the
credential level is encoded in the first attribute of the credential (after the
\usk), which we denote with $a_1$. In this context, any owner of a credential of
level $n$ can define an issuance function $\fissue^n$, as in
\eref{eq:uas-delcred-func}. Similarly, we may just have the signing evaluation
function reveal the level of each credential used for signing, along with any
other desired attribute, as in $\feval^{\dattrs,n}$, in
\eref{eq:uas-delcred-func}. Note that it is straightforward to create more
complex functions in both cases which, for instance, also take into account
roles, or hiding the level but ensuring that it meets whatever desired rules.

\begin{align}
  & \fissue^n(\usk,\scred,\attrs) \coloneqq \lbrace \pcif a_1 = n+1: \pcreturn 1;
  \pcelse \pcreturn 0 \rbrace \nonumber \\
  & \feval^{\dattrs,n}(\usk,\scred,\msg) \coloneqq \lbrace \pcreturn
    \dattrs(\scred),a_1(\scred) \rbrace  
  \label{eq:uas-delcred-func}
\end{align}
